Appendix A: Stochastic simulations of noisy phenomena

### 2017-11-01 appendixA/appendixA.Rmd
try without cache please
try without bquote text?

```{r echo=FALSE}
## plot themes, non-essential. Comment out if theme creates trouble with fonts on your system.
library(hrbrthemes)
library(extrafont)
extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
hrbrthemes::import_roboto_condensed()   # One-time use to set up fonts

d <- read.csv(extrafont:::fonttable_file(), stringsAsFactors = FALSE)
d[grepl("Light", d$FontName), ]$FamilyName <- "Roboto Condensed Light"
write.csv(d, extrafont:::fonttable_file(), row.names = FALSE)

@@

p1 <- read_csv("../appendixA/noisy_switch.csv")  %>%
  ggplot(aes(t,x)) + 
  geom_line(lwd=.1, col=colours[[1]]) +
  labs(subtitle = bquote(bold(A.)))

p2 <-  theory %>%
  ggplot(aes(x, y, col=curve)) +
  geom_line(lwd=1) + 
  scale_color_ptol() + 
  labs(x = bquote(X[t]), y = bquote(X[t+1]), subtitle= bquote(bold(B.))) +
  theme(legend.position="top")

p3 <-  theory %>%
  ggplot(aes(x, potential)) + 
  geom_line(col=colours[1], lwd=1) + 
  coord_cartesian(xlim=c(0,1.6), ylim=c(-1.15,-0.9)) + 
  labs(subtitle = bquote(bold(C.)))

>>>>

```{r echo=FALSE}
## plot themes, non-essential. Comment out if theme creates trouble with fonts on your system.
library(hrbrthemes)
library(extrafont)
#extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
hrbrthemes::import_roboto_condensed()   # One-time use to set up fonts

#d <- read.csv(extrafont:::fonttable_file(), stringsAsFactors = FALSE)
#d[grepl("Light", d$FontName), ]$FamilyName <- "Roboto Condensed Light"
#write.csv(d, extrafont:::fonttable_file(), row.names = FALSE)

@@

p1 <- read_csv("../appendixA/noisy_switch.csv")  %>%
  ggplot(aes(t,x)) + 
  geom_line(lwd=.1, col=colours[[1]]) +
  labs(subtitle = "A.")

p2 <-  theory %>%
  ggplot(aes(x, y, col=curve)) +
  geom_line(lwd=1) + 
  scale_color_ptol() + 
 labs(
 #  x = bquote(X[t]), y = bquote(X[t+1]), 
   subtitle= "B.") +
  theme(legend.position="top")

p3 <-  theory %>%
  ggplot(aes(x, potential)) + 
  geom_line(col=colours[1], lwd=1) + 
  coord_cartesian(xlim=c(0,1.6), ylim=c(-1.15,-0.9)) + 
  labs(subtitle = "C.")
